hormones

### 2019-10-11 analysis/07_hormones.Rmd
all four hormones

hormonecharplot("prolactin", "PRL (ng/mL)")

a <- hormonecharplot("estradiol", "E (ng/mL)")
b <- hormonecharplot("testosterone", "T (ng/mL)")

c <- hormonecharplot("cort", "CORT (ng/mL)")
d <- hormonecharplot("progesterone", "PROG (ng/mL)")

e <- hormonecharplot("prolactin", "PRL (ng/mL)") + theme(legend.position = "right", legend.direction = "horizontal")

cd <- plot_grid(d,c, nrow = 2)
ab <- plot_grid(a,b, nrow = 2)

abcd <- plot_grid(cd,ab, rel_widths = c(0.6,0.4))
plot_grid(e,abcd, ncol = 1)

>>>>

a <- hormonecharplot("prolactin", "PRL (ng/mL)")
b <- hormonecharplot("cort", "CORT (ng/mL)")
c <- hormonecharplot("progesterone", "PROG (ng/mL)") 
d1 <- hormonecharplot("estradiol", "E (ng/mL)")
d2 <- hormonecharplot("testosterone", "T (ng/mL)")
d <- plot_grid(d1,d2, nrow = 1)
abcd <- plot_grid(a, b ,c, d)
mylegend <- get_legend(c + theme(legend.position = "bottom"))
plot_grid(abcd, mylegend, nrow = 2, rel_heights = c(0.85,0.15))
```
